Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-25 paper/agujournaltemplate.tex
Added release reference

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. We also would like to thank Charles Sammis and an anonymous reviewer whose reviews have helped improve the paper. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5062659}.

>>>>

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. We also would like to thank Charles Sammis and an anonymous reviewer whose reviews have helped improve the paper. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5725990}.
